### 2015-11-05 Assignment IV/Assignment4-Ditz_Schroeder-WS15-16.tex
Exercise final.
aufgabe 1 überarbeitet; jetzt mit DP matrix

\usepackage[T1]{fontenc} % T1 Schrift Encoding
\usepackage{textcomp}    % Zusatzliche Symbole (Text Companion font extension)
\usepackage{lmodern,dsfont}     % Latin Modern Schrift
\usepackage{dsfont}
%\usepackage{wasysym}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{grffile} %allows to use pngs
\usepackage{eurosym}
%\usepackage{txfonts}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{listings}
\usepackage{etextools}
\usepackage{ifthen}
%\usepackage{TikZ} %phylogenetischer Baum
%\usetikzlibrary{calc, shapes, backgrounds} %für die Phylogenetische bäume
%\usetikzlibrary{automata,arrows}
\usepackage{subfigure}

@@

\noindent If we fill the DP matrix using this recursion, we get the following MSA:

@@

The last step was creating the actual MSA. The 'complete alignment' methode 
\begin{figure}[h]
	\includegraphics[width=\textwidth]{Img/Exercise2-CompleteAlignment.png}
	\caption{ Complete alignment methode is used to get an MSA from the guidetree from step 2	}
	\label{completealign}
\end{figure}
\section*{Practical Assignment - \textsl{Comparing multiple alignment}}

>>>>

\usepackage[T1]{fontenc} % T1 Schrift Encoding
\usepackage{textcomp}    % Zusatzliche Symbole (Text Companion font extension)
\usepackage{lmodern,dsfont}     % Latin Modern Schrift
\usepackage{dsfont}
\usepackage{color}
%\usepackage{wasysym}
\usepackage{ulem}
\usepackage{graphicx}
\usepackage{grffile} %allows to use pngs
\usepackage{eurosym}
%\usepackage{txfonts}
\usepackage{stmaryrd}
\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{tikz}
\usepackage{multirow}
\usepackage{listings}
\usepackage{etextools}
\usepackage{ifthen}
%\usepackage{TikZ} %phylogenetischer Baum
%\usetikzlibrary{calc, shapes, backgrounds} %für die Phylogenetische bäume
%\usetikzlibrary{automata,arrows}
\usepackage{subfigure}

@@

\noindent Such a recursion results in a three-dimensional matrix. Since such a matrix is really difficult to 
sketch, we split it into three two-dimensional matrices.

\begin{figure}[ht]
\centering
\subfigure{
\begin{tabular}{c|cccc}
 0 & 0 & C & C & T \\
 \hline
 0 & \textcolor{red}{\textbf{0}} & -2 & -4 & -6 \\
 C & -2 & \textcolor{red}{\textbf{-2}} & -4 & -10 \\
 T & -4 & -8 & -8 & -6 \\
 T & -6 & -10 & -12 & -10 \\
\end{tabular}}
\subfigure{
\begin{tabular}{c|cccc}
 T & 0 & C & C & T \\
 \hline
 0 & -2 & -4 & -6 & -8 \\
 C & -4 & -4 & -6 & -10 \\
 T & -6 & -8 & \textcolor{red}{\textbf{-4}} & 2 \\
 T & -8 & -10 & -8 & 2 \\
\end{tabular}}
\subfigure{
\begin{tabular}{c|cccc}
 C & 0 & C & C & T \\
 \hline
 0 & -4 & -6 & -8 & -10 \\
 C & -6 & 2 & 2 & -8 \\
 T & -8 & -6 & -2 & 0 \\
 T & -10 & -8 & -6 & \textcolor{red}{\textbf{-6}} \\
\end{tabular}}
\caption[DP matrix of MSA]{DP matrix of MSA, traceback is shown in red}
\end{figure}

\noindent If we fill the DP matrix using this recursion, we get several optimal alignments. One of 
them is the following:

@@

The last step was creating the actual MSA. The 'complete alignment' methode was used. This means after every step, the distance of the new sequences was determined to each other sequence in the cluster. The optimal resulting score was used to get the best alignment for the new Sequence. after 3 steps the MSA was completed. (figure \ref{completealign})
\begin{figure}[h]
	\includegraphics[width=\textwidth]{Img/Exercise2-CompleteAlignment.png}
	\caption{ Complete alignment methode is used to get an MSA from the guidetree from step 2	}
	\label{completealign}
\end{figure}
\section*{Practical Assignment - \textsl{Comparing multiple alignment}}
